---
title: "Regression_county_elast"
output: html_document
---


<style>
.main-container {
  max-width: 1800px !important;
}

.vscroll-plot {
    height: 600px;
    overflow-y: scroll;
    overflow-x: scroll;
}

.TableDiv {
    height: 600px;
    overflow-y: scroll;
    overflow-x: scroll;
}
</style>

```{r, include=FALSE}

rm(list=ls())
library(readr)
library(tidyr)
library(dplyr)
library(data.table)
library(stringi)
library(fixest)
library(countrycode)
library(tidyverse)
library(vroom)
library(readr)
library(dplyr)
library(sf)
library(tigris)
library(ggplot2)
library(viridis)

################################################################################
# LOad data 
dta <- read_csv("/data/sikeme/TRADE/US_CHN_TradeWar_git/data/Pop_reg_dta/merge_elast_subsector_county.csv")
names(dta)
table(dta$year)
exp <- "/data/sikeme/TRADE/US_CHN_TradeWar_git/output/step_2/regression/elast/county/epop/"
################################################################################

sub_dta <- dta %>% filter(year %in% c(2016:2019))
names(sub_dta)

```



In each of the regression we look at the time period from 2018 to 2019. 
The controls are change in outcome variable in a prepriod (chenge in the outcome fromm 2016 to 2017). 


# Employment to population ratio  {.tabset}
```{r}
reg1 <- feols(change_EPOP_2017_bis ~ IMP_tariff_r + RET_tariff_r + RET_NTB_IV_r |
                year, data = sub_dta, weights = ~emp_2012, cluster ~fips)

reg2 <- feols(change_EPOP_2017_bis ~ IMP_tariff_r + RET_tariff_r + RET_NTB_IV_r +
                SUB + as.factor(year):share_crop + as.factor(year):share_livestock + as.factor(year):share_nonag +
                as.factor(year):share_forestry   |
                year, data = sub_dta, weights = ~emp_2012, cluster ~fips)

reg3 <- feols(change_EPOP_2017_bis ~ IMP_tariff_r + RET_tariff_r + RET_NTB_IV_r +
                SUB + as.factor(year):share_crop + as.factor(year):share_livestock + as.factor(year):share_nonag +
                as.factor(year):share_forestry +
                as.factor(division):as.factor(year) |
                year, data = sub_dta, weights = ~emp_2012, cluster ~fips)

reg4 <- feols(change_EPOP_2017_bis ~ IMP_tariff_r + RET_tariff_r + RET_NTB_IV_r +
                SUB + as.factor(year):share_crop + as.factor(year):share_livestock + as.factor(year):share_nonag +
                as.factor(year):share_forestry +
                as.factor(division):as.factor(year) + year:change_EPOP_2017_2016 |
                year, data = sub_dta, weights = ~emp_2012,  cluster ~fips)

tbl <- etable(reg1, reg2, reg3, reg4,
              headers = c("(1)", "(2)", "(3)", "(4)"),
              drop    = c("share_ag_mining", "share_mfg", "share_other",
                          "division", "change_EPOP_2017_2016"),
              digits  = 4,
              fitstat = ~ n + r2 + ar2 + f + f.p + rmse,
              extralines = list(
                "-^Year FE"                        = list("Yes", "Yes", "Yes", "Yes"),
                "-^Sector x year-month FE"               = list("No",  "Yes", "Yes", "Yes"),
                "-^Census division x year-month FE"      = list("No",  "No",  "Yes", "Yes"),
                "-^Pre-trend CZ outcome 2017"            = list("No",  "No",  "No",  "Yes")
              ))
tbl
```


# Wage  {.tabset}



# Employment  {.tabset}



# H2A employment  {.tabset}




