---
title: "regression_sector_specific"
output:
  html_document:
    css: styles.css
---

```{r, include = FALSE}
rm(list=ls())

library(readr)
library(tidyr)
library(dplyr)
library(data.table)
library(stringi)
library(fixest)
library(countrycode)
library(tidyverse)
library(vroom)
library(sf)
library(tigris)
library(ggplot2)
library(viridis)
library(kableExtra)
library(corrplot)

################################################################################
# Load data
dta <- read_csv("/data/sikeme/TRADE/US_CHN_TradeWar_git/data/Pop_reg_dta/merge_elast_subsector_county_sector_specific.csv")
exp <- "/data/sikeme/TRADE/US_CHN_TradeWar_git/output/step_2/regression/"
```

<style>
.main-container {
  max-width: 1800px !important;
}

.vscroll-plot {
    height: 600px;
    overflow-y: scroll;
    overflow-x: scroll;
}

.TableDiv {
    height: 600px;
    overflow-y: scroll;
    overflow-x: scroll;
}
</style>

```{r setup-functions, echo = FALSE}
sub_dta <- dta %>% filter(year %in% c(2018:2019))

# ---------------------------------------------------------------------------
# Helpers: everything that used to be copy-pasted per subsector lives here.
# A "sector" is identified by its suffix (crop / livestock / nonag). All the
# sector-specific variable names are built from that suffix.
# ---------------------------------------------------------------------------

# Build the analysis frame for one outcome x subsector
build_sector_dta <- function(data, outcome, sub) {
  vars <- c(
    "year", "fips", "division", outcome,
    paste0("IMP_tariff_tot_ir_", sub),
    paste0("RET_tariff_tot_r_", sub),
    paste0("RET_NTB_tot_r_", sub),
    paste0("RET_NTB_tot_IV_r_", sub),
    "SUB",
    paste0("share_", sub),
    paste0(outcome, "_pretrend")
  )
  data %>%
    filter(subsector == sub) %>%
    select(all_of(vars))
}

# Correlation plot (drops the id columns before correlating)
plot_sector_cor <- function(d) {
  cm <- d %>%
    select(-year, -fips) %>%
    cor(use = "complete.obs")
  corrplot(cm, method = "circle", addCoef.col = "black",
           number.cex = 0.6, tl.cex = 0.8)
}

# Run the four nested specifications.
#   iv          : use the IV-constructed NTB variable instead of the raw one
#   include_sub : add SUB to the RHS (TRUE for crop/livestock, FALSE for nonag)
run_sector_reg <- function(d, outcome, sub, iv = FALSE, include_sub = TRUE) {
  imp   <- paste0("IMP_tariff_tot_ir_", sub)
  ret   <- paste0("RET_tariff_tot_r_", sub)
  ntb   <- paste0(if (iv) "RET_NTB_tot_IV_r_" else "RET_NTB_tot_r_", sub)
  share <- paste0("share_", sub)
  pre   <- paste0(outcome, "_pretrend")

  core <- paste(imp, "+", ret, "+", ntb, if (include_sub) "+ SUB" else "")
  rhs2 <- paste(core, "+ as.factor(year):", share)
  rhs3 <- paste(rhs2, "+ as.factor(division):as.factor(year)")
  rhs4 <- paste(rhs3, "+ year:", pre)

  f <- function(rhs) as.formula(paste(outcome, "~", rhs, "| year"))

  list(
    feols(f(core), data = d, cluster = ~fips),
    feols(f(rhs2), data = d, cluster = ~fips),
    feols(f(rhs3), data = d, cluster = ~fips),
    feols(f(rhs4), data = d, cluster = ~fips)
  )
}

# Format the four models into the styled table
sector_table <- function(models) {
  etable(models[[1]], models[[2]], models[[3]], models[[4]],
         headers = c("(1)", "(2)", "(3)", "(4)"),
         digits  = 4,
         fitstat = ~ n + r2 + ar2 + f + f.p + rmse,
         extralines = list(
           "-^Year FE"                         = as.list(rep("Yes", 4)),
           "-^Sector x year-month FE"          = list("No", "Yes", "Yes", "Yes"),
           "-^Census division x year-month FE" = list("No", "No",  "Yes", "Yes"),
           "-^Pre-trend CZ outcome 2017"       = list("No", "No",  "No",  "Yes")
         )) %>%
    kable() %>%
    kable_styling(full_width = TRUE)
}

# Convenience wrapper: OLS table then IV table for one outcome x subsector.
# nonag is detected automatically to drop SUB.
sector_tables <- function(d, outcome, sub) {
  inc <- sub != "nonag"
  list(
    ols = sector_table(run_sector_reg(d, outcome, sub, iv = FALSE, include_sub = inc)),
    iv  = sector_table(run_sector_reg(d, outcome, sub, iv = TRUE,  include_sub = inc))
  )
}
```

# Employment to population ratio  {.tabset}

## Crop sector    {.tabset}

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_EPOP", "crop")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_EPOP", "crop")
tabs$ols
tabs$iv
```

## Livestock sector

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_EPOP", "livestock")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_EPOP", "livestock")
tabs$ols
tabs$iv
```

## non ag

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_EPOP", "nonag")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_EPOP", "nonag")
tabs$ols
tabs$iv
```

# Log employment change  {.tabset}

## Crop sector    {.tabset}

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_log_emp", "crop")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_log_emp", "crop")
tabs$ols
tabs$iv
```

## Livestock sector

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_log_emp", "livestock")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_log_emp", "livestock")
tabs$ols
tabs$iv
```

## non ag

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_log_emp", "nonag")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_log_emp", "nonag")
tabs$ols
tabs$iv
```

# Log wage change  {.tabset}

## Crop sector    {.tabset}

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_log_wages", "crop")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_log_wages", "crop")
tabs$ols
tabs$iv
```

## Livestock sector

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_log_wages", "livestock")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_log_wages", "livestock")
tabs$ols
tabs$iv
```

## non ag

```{r, echo = FALSE}
d <- build_sector_dta(sub_dta, "delta_log_wages", "nonag")
plot_sector_cor(d)
tabs <- sector_tables(d, "delta_log_wages", "nonag")
tabs$ols
tabs$iv
```
